Data Processing (Julia)

### 2025-05-03 notebooks/01_results_julia.qmd
update

```{julia}
using Juno
using Juno: r_map, datalimits_f
using CairoMakie: WilkinsonTicks
using CairoMakie.Makie: resize_to_layout!
using DrWatson
using Discontinuity
using AlgebraOfGraphics
using DataFramesMeta
using Beforerr
import Beforerr: easy_save
using LaTeXStrings
M = var_mapping(; log_str="")

@@

>>>>

```{julia}
using Juno
using Juno: r_map, datalimits_f, produce_or_load_juno
using CairoMakie
using CairoMakie: WilkinsonTicks
using CairoMakie.Makie: resize_to_layout!
using DrWatson
using Discontinuity
using Discontinuity: var_mapping, compute_params!, compute_orientation_params!, filter_low_mva_quality!
using AlgebraOfGraphics
using DataFramesMeta
using Beforerr
import Beforerr: easy_save
using LaTeXStrings
using Unitful
M = var_mapping(; log_str="")

@@

### Orientation

```{julia}
# ds = produce_or_load_juno()
let df= dropmissing(ds), color = r_map
    @chain df begin
        compute_orientation_params!
        filter_low_mva_quality!
    end
    f = Figure()
    spec = data(df) * mapping(:B_n_mva_norm, :B_n_cross_norm) * AlgebraOfGraphics.density()
    draw!(f[1,1],spec)
    spec2 = data(df) * mapping(:θ_mva_cross) * AlgebraOfGraphics.density()
    draw!(f[1,2],spec2)
    f
end
```

### 2025-05-03 notebooks/21_model.qmd
update

```{julia}
using Discontinuity
using Discontinuity: Alfven_current
using PlasmaFormulary: inertial_length
@quickactivate
include("../src/main.jl")
```

```{julia}
using DrWatson: datadir
using DataFrames, DataFramesMeta
using Unitful
using Juno.Data: read_sw_params_csv

jno_sw_params = read_sw_params_csv()
```

```{julia}
using FlexiJoins
using Distances
using Dates
using Unitful: μ0

jno_df_with_params = innerjoin(
    (jno_df, jno_sw_params),
    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :UTC);
)

@chain jno_df_with_params begin
    @transform! begin
        :d_star = :d_star .* u"nT/s"
        :duration = :duration .* u"s"
        :V_KMPS = :V_KMPS .* u"km/s"
    end
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :j_Alfven_sw = Alfven_current.(:b_mag, :N_PROTONS_CC)
    end
    @transform! begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :j0_k_sw = @. abs(:d_star / :V_n_cross_sw / μ0) |> u"nA/m^2"
    end
    @transform! begin
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :j0_k_sw_norm = @. :j0_k_sw / :j_Alfven_sw |> NoUnits
    end
end
```

```{julia}
using CairoMakie
using UnitfulLatexify: latexroundunitlabel as lru

let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno"
    f = Figure()
    ax = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
    scatter!(ax, norm.(df[!, :V]), ustrip.(df[!, :V_KMPS]))

    ax2 = f[1, 2] = Axis(f; title=lru("n", u"cm^-3"), xscale=log10, yscale=log10)
    scatter!(ax2, ustrip.(df[!, :n]), ustrip.(df[!, :N_PROTONS_CC]))
    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale=log10, yscale=log10)
    scatter!(ax3, ustrip.(df[!, :L_n_cross]), ustrip.(df[!, :L_n_cross_sw]))
    ax4 = f[2, 2] = Axis(f; title=lru("J", u"nA/m^2"), xscale=log10, yscale=log10)
    scatter!(ax4, ustrip.(df[!, :j0_k]), ustrip.(df[!, :j0_k_sw]))
    ax5 = f[3, 1] = Axis(f; title=L"L/d_i", xlabel, ylabel, xscale=log10, yscale=log10)
    scatter!(ax5, df[!, :L_n_cross_norm], df[!, :L_n_cross_sw_norm])
    ax6 = f[3, 2] = Axis(f; title=L"J/J_{Alfven}", xlabel, xscale=log10, yscale=log10)
    scatter!(ax6, df[!, :j0_k_norm], df[!, :j0_k_sw_norm])
    for ax in (ax,)
        ablines!(ax, 0, 1, color=:red, linestyle=:dash)
    end

@@

>>>>

```{julia}
using Discontinuity
using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current
using Juno: produce_or_load_juno
using PlasmaFormulary: CurrentDensity, NumberDensity
```

```{julia}
using DataFrames, DataFramesMeta
using Unitful
using Juno.Data: read_sw_params_csv

jno_df = produce_or_load_juno()
jno_sw_params = read_sw_params_csv(; add_unit=true)
```

```{julia}
using FlexiJoins
using Dates
using Unitful: μ0

jno_df_with_params = innerjoin(
    (jno_df, jno_sw_params),
    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :time);
)

@chain jno_df_with_params begin
    compute_params!
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :V_n_mva_sw = @. abs(first(:n_mva) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
    end
    @transform! @astable begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :L_n_mva_sw = :V_n_mva_sw .* :duration
        :L_n_mva_sw_norm = @. :L_n_mva_sw / :d_i_sw |> NoUnits
        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits
        :J_m_max_mva_sw = @. abs(gradient_current(:grad, :V_n_mva_sw))
        :J_m_max_mva_sw_norm = @. :J_m_max_mva_sw / :J_A_sw |> NoUnits
    end
end
```

```{julia}
using CairoMakie
using UnitfulLatexify: latexroundunitlabel as lru
using CairoMakie.GeometryBasics

p_big = decompose(Point2f, Circle(Point2f(0), 1))
p_small = decompose(Point2f, Circle(Point2f(0), 0.5))

uless(x) = NoUnits(x)
uless(x::NumberDensity) = NoUnits(x / u"cm^-3")
uless(x::CurrentDensity) = NoUnits(x / u"nA/m^2")
uless(x::Unitful.Length) = NoUnits(x / u"km")
uless(x::Unitful.Velocity) = NoUnits(x / u"km/s")

let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", xscale = log10, yscale = log10, plot = (; alpha=0.3)
    f = Figure(; size=(600, 600))
    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), xscale, yscale)
    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale, yscale)
    ax4 = Axis(f[2, 2]; title=lru("J", u"nA/m^2"), xscale, yscale)
    ax5 = Axis(f[3, 1]; title=L"L/d_i", xlabel, ylabel, xscale, yscale)
    ax6 = Axis(f[3, 2]; title=L"J/J_{Alfven}", xlabel, xscale, yscale)

    p1, p2 = @with df begin
        scatter!(ax1, uless.(:V_mag), uless.(:V_KMPS))
        scatter!(ax2, uless.(:n), uless.(:N_PROTONS_CC))

        p1 = scatter!(ax3, uless.(:L_n_cross), uless.(:L_n_cross_sw), label="Cross"; plot...)
        p2 = scatter!(ax3, uless.(:L_n_mva), uless.(:L_n_mva_sw), label="MVA"; plot...)

        scatter!(ax4, uless.(:J_m_max_cross), uless.(:J_m_max_cross_sw), label="Cross"; plot...)
        scatter!(ax4, uless.(:J_m_max_mva), uless.(:J_m_max_mva_sw), label="MVA"; plot...)

        scatter!(ax5, uless.(:L_n_cross_norm), uless.(:L_n_cross_sw_norm); plot...)
        scatter!(ax5, uless.(:L_n_mva_norm), uless.(:L_n_mva_sw_norm); plot...)
        scatter!(ax6, uless.(:J_m_max_cross_norm), uless.(:J_m_max_cross_sw_norm); plot...)
        scatter!(ax6, uless.(:J_m_max_mva_norm), uless.(:J_m_max_mva_sw_norm); plot...)
        (p1, p2)
    end

    Legend(f[1, 3], [p1, p2], ["Cross", "MVA"])

    for ax in (ax1,)
        ablines!(ax, 0, 1, color=:red, linestyle=:dash)
    end

@@

    limits!(ax1, 360, 550, 360, 550)

### 2025-05-03 notebooks/30_data.qmd
update

```{julia}
using Juno.Data
using DimensionalData

@@

```{julia}
using Discontinuity
using Dates
using DataFrames
period = Second(60)

ds = mapreduce(vcat, 2011:2016) do year
    b = get_mag_data(year)
    ids_finder(b, period, V, n)
end
```

```{julia}
using FlexiJoins
using StaticArrays
ds.r = r[Ti(Near(ds.time))]
ds.T = T[Ti(Near(ds.time))] * u"K"

>>>>

```{julia}
using Juno: produce_or_load_juno
using Juno.Data
using DimensionalData

@@

```{julia}
using Discontinuity
using Dates
using DataFrames

ds = produce_or_load_juno()
```

```{julia}
using FlexiJoins
using StaticArrays
ds.r = parent(r[Ti(Near(ds.time))])
ds.T = T[Ti(Near(ds.time))] * u"K"
